Falls are one of the leading causes of fatal and non-fatal injuries especially for elderly people in today's society. Quick response is vital to reducing the long-term effects on the victim physically, emotionally and mentally \citep{dangerousFalls,stokesFall}. Falls have been one of leading cause of injuries across all age groups placing a strain on health and financial systems around the world. \par
As a result, an efficient, accurate and cost effective detection system needs to be implemented for a variety of environments. Over 50\% of falls for the 65+ age group (1/3 experience a fall at least once a year) occur in their home so a solution that is \textbf{cheap, accurate, privacy-focused} and \textbf{easily installed} is needed \citep{medicalFall, stokesFall}. 
Personally, I have seen the effects falls can have on an elderly person and the fear induced in a fall victim post-treatment can deem them unable to live alone again. \citep{fearFall} \par
There are a number of solutions on the commercial market today which can be divided into a broad number of categories: Wearables, Visual, Ambient Environment. Products on the market in these categories include the Apple Watch, cameras, accelerometer belts, floor vibration sensors and infrared devices. \textbf{Privacy} is a key issue that needs to be addressed across the world in the next decade. Therefore, it was a key aim of my project to keep it as privacy oriented as possible. Many of the current solutions on the market suffer from privacy issues especially in such a sensitive environment as somebody's home. Many of these off-the-shelf solutions require \textbf{Direct Line of Sight (LOS)} to the person in the room to detect a fall. No obstacles can be in the way of the detection apparatus or a fall may not be detected by the system. This is especially useless in a busy household environment with many obstacles. All of these existing solutions are \textbf{very expensive} to buy and implement such as the Apple Watch, specialist cameras and Man-Down alarms. Another issue arises as elderly people are not inclined to wear them as they hinder them from daily activities and can feel like a chore to keep them charged/around their neck or waist. This results in a lot of people refusing to wear them which is clearly unsatisfactory as a solution. More complex solutions such as Computer Vision cameras require \textbf{high processing power} as the calculations and classification operations needed for the sheer amount of data recovered in any of these fall detection experiments. \par
Therefore, I propose a Wi-Fi based solution utilising commercial off the shelf (COTS) Wi-Fi network cards providing a cheap, highly accurate and non-intrusive fall detection system for the home and other environments. A fall is detected accurately and privately due to the rich multi-path environment that exists between a number of transmitting and receiving antennas. \par
\begin{comment}Previous research papers have explored the use of the Channel State Information (CSI) of a WLAN Channel for fall detection.\end{comment} 
The aims of the project/project plan are as follows: 
\vspace{-11pt}
\begin{itemize}[noitemsep, topsep=0pt]
\item Gain a strong understanding and background of CSI in the \textit{IEEE802.11n} Wi-Fi standard 
\item Build an initial system which can collect CSI using the Intel Wi-Fi Link 5300 NIC for a range of Transmitter-Receiver setups
\item Obtain CSI data for a range of human activities which would be typical in home/workplace environments
\item Design, build and test signal processing algorithms to clean the CSI data obtained for fall detection under various conditions
\item Design, implement and test various Machine Learning/Classification algorithms for fall detection for a target fall detection rate of $>$90\%
\end{itemize}
\begin{comment}
\begin{center}
\begin{tabular}{|c||p{10cm}|}
 \hline
 \multicolumn{2}{|c|}{\textbf{Project Timeline}} \\
 \hline
 \bfseries Date & \bfseries Task to be completed \\
 \hline
 19/09/19 & Allocation of Projects \\
 23/09 - 14/10 & Research OFDM, 802.11n, CSI \& Current State of the Art \\
 14/10 - 28/10 & Gather CSI data using Intel NIC under various activities, conditions \& environments \\ 
 28/10 - 18/11 & Researching, developing \& implementing signal processing algorithms to clean the CSI data for feature extraction \\
 26/11 & Interim Presentation \\
 27/11 - 6/12 & Gather data under more use cases \\
 03/01/20 - 15/01/20 & Identify features for activity segmentation of CSI data \\
 15/01 - 19/01 & Obtain much larger CSI datasets ($>$15mins of data) \\
 20/01 & Interim Report submission \\
 22/01 - 29/01 & Implement Activity Segmentation methods \\
 01/02 - 28/02 & Research, design \& implement different classification methods for fall detection \\
 29/02 - 22/03 & Test and tune classification methods for optimal fall detection accuracy \\
 27/03 & Conference Paper and Critique submission \\
 24/04 & Final Project Report Submission \\
 \hline
\end{tabular}
\end{center}
\end{comment}